XRONOS: an open infrastructure for archaeological chronometric data

### 2024-07-29 paper.qmd
Rewrite for JCAA

- Max 8000 words including all figures etc.
- Max 6 figures/tables
- Abstract max 100 words
- Max 10 keywords
- Word 2002 or earlier or RTF (???)
- Tables seperately in XLS
- Figures seperately in TIFF or EPS
- double spaced, wide
  -->

>>>>

- Max 8000 words including all figures etc.
- Max 6 figures/tables
- Abstract max 100 words
- Max 10 keywords
- Word 2002 or earlier or RTF (???)
- Tables seperately in XLS
- Figures seperately in TIFF or EPS
- double spaced, wide

OR as a JCAA 'case study' - 5,000 words
  -->
